%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Mohammad-Mohsen}{Aseman-Manzar}{ % Your name
\href{mailto:m.m.asemanmanzar@gmail.com}{m.m.asemanmanzar@gmail.com} | 
Github:// \href{https://github.com/mohsenasm}{\bf mohsenasm} |
\href{https://www.linkedin.com/in/asemanmanzar}{\bf LinkedIn} |
\href{https://asemanmanzar.ir}{\bf asemanmanzar.ir}
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Sharif University of \\ Technology}

\descript{Ph.D. in Computer Engineering}
\location{2020 - Present}
\location{Direct Admission, GPA: 18.98 / 20.0}
{\footnotesize \textit{Thesis: Preserving Privacy in The Internet of Things to The Level of Events Unlinkability: Smart Home Case Study }} \\

\sectionspace % Some whitespace after the section

\subsection{Sharif University of \\ Technology}

\descript{MSc. in Computer Engineering, Software}
\location{2018 - 2020}
\location{Direct Admission, GPA: 19.15 / 20.0}
{\footnotesize \textit{Thesis: Big Data Application Performance Prediction and Cost-based Heterogeneous Resource Recommendation in Cloud}} \\

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Iran University of Science \& Technology}

\descript{BSc. in Computer Engineering, Software}
\location{2014 - 2018}
\location{First Rank, GPA: 18.76 / 20.0}
{\footnotesize \textit{Final Project: Mixed Performance and Power Consumption Modeling in Virtual Machine Using Coloured Petri Nets}} \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

%\section{Links} 
%
%Github:// \href{https://github.com/mohsenasm}{\bf mohsenasm} \\
%LinkedIn:// \href{https://www.linkedin.com/in/asemanmanzar}{\bf asemanmanzar} \\
%https:// \href{https://asemanmanzar.ir}{\bf asemanmanzar.ir} \\
%
%\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}
System Analysis and Design |
Software Engineering |
Computer System Performance Evaluation |
Formal Specification and Verification of Programs |
Object-Oriented Analysis and Design |
Formal Methods in Software Engineering |
Software Testing |
Operating Systems |
Computer Networks |
Artificial Intelligence and Expert Systems |
Data Mining | Machine Learning Privacy and Security

{\footnotesize \textit{\textbf{Teacher Assistant: }}} \\

Theory of Distributed Systems |
Verification of Reactive Systems |
Algorithmic Game Theory |
Advanced Programming

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}
Python \textbullet{} Go \textbullet{} JavaScript \textbullet{} Rust \textbullet{} Swift \\ %\textbullet{} 
C\# \textbullet{} C/C++ \textbullet{} Java \textbullet{} SQL \textbullet{} Flask \textbullet{} Gin \\ %\textbullet{} 
React \textbullet{} NumPy \textbullet{} PyTorch \textbullet{} Unity3D \\ %\textbullet{} 
Redis \textbullet{} PostgreSQL \textbullet{} MongoDB \\ %\textbullet{} 
CockroachDB \textbullet{} Spark \textbullet{} Git \textbullet{} Figma  \\ %\textbullet{} 
Docker-Swarm \textbullet{} K8s (Kubernetes) 
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Hinava Smart Home}
\descript{| Senior Software Developer \& Solution Architect}

\location{Jul 2016 - Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Joined as an {\bf iOS developer}, later transitioning to the {\bf backend team} to rewrite the backend stack for improved uptime and stability. I then moved into the role of {\bf Solution Architect}, where I designed and developed the architecture of the smart home system, ensuring seamless integration and user-friendly functionality across all devices.
\item Developed the iOS client application using {\bf Swift}, and also developed the web application client using {\bf React} and {\bf JavaScript}, supporting Android, iOS, and web platforms, featuring a comprehensive interface with 50 pages.
\item Designed \& Developed a backend architecture consisting of 30 {\bf microservices} based on {\bf Docker Swarm}, which was later migrated to {\bf Kubernetes} for improved stability and orchestration.
\item Collaborated with the backend team to develop the stack using {\bf Python} and {\bf Golang}, utilizing frameworks like Flask and Gin, while promoting clean code practices and knowledge sharing through code reviews and pair programming.
\item Designed {\bf highly available architecture} for the backend stack using {\bf CockroachDB}, {\bf HAProxy}, {\bf ActiveMQ}, {\bf Redis}, and {\bf OpenStack}.
\item Developed an enhanced service monitoring \& alerting dashboard using {\bf Grafana}, {\bf Prometheus}, {\bf Kibana}, and {\bf Elasticsearch}.
\item Developed a comprehensive test suite that includes unit tests, system tests, and integration with GitLab {\bf CI/CD}, implementing effective {\bf DevOps} strategies.

\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Hamayeh}
\descript{| iOS Developer}

\location{Aug 2015 - Feb 2016}
\begin{tightitemize}
\item Developed the iOS application to connect to the Axiom smart home system, which utilized Zigbee technology.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Elmogame Game Studio}
\descript{| Client/Server Developer}

\location{Sep 2014 - Sep 2019}
\begin{tightitemize}
\item Contributed as a {\bf Unity3D} developer and backend developer on three published Android games (Farmuler, Footyard, and NewCity), focusing on online gameplay, custom physics engine, and AI, utilizing Python, {\bf C\#}, {\bf PostgreSQL}, Docker, Unity3D, and {\bf RabbitMQ}.
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------

\runsubsection{Open-Source Contributions}
\descript{}
\nolocation
\begin{tightitemize}
\item Maintainer of the \href{https://github.com/mohsenasm/swarm-dashboard}{\bf swarm-dashboard} project, a monitoring dashboard for docker swarm cluster.
\item Merged pull requests on:
\vspace{0.2cm}
\begin{tightitemize}
\item \href{https://github.com/k0sproject/k0s}{\bf k0sproject/k0s}{\footnotesize , An All-Inclusive Kubernetes Distribution.}
\item \href{https://github.com/cockroachdb/cockroach-operator}{\bf cockroachdb/cockroach-operator}{\footnotesize , K8s Operator for CockroachDB.}
\item \href{https://github.com/espressif/esp-idf}{\bf espressif/esp-idf}{\footnotesize , Development Framework for Espressif SoCs.}
\item \href{https://github.com/robinrodricks/vue3-touch-events}{robinrodricks/vue3-touch-events}{\footnotesize , A Touch-Support Plugin for Vue.js 3.}
\end{tightitemize}
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Research
%------------------------------------------------

\section{Publication}

\location{IEEE Transactions on Services Computing, vol. 16, no. 3, pp. 1726-1737, 1 May-June 2023}
\href{https://ieeexplore.ieee.org/document/9894699}{Cost-aware Resource Recommendation for DAG-based Big Data Workflows: Apache Spark Case Study}

\sectionspace % Some whitespace after the section

\location{IEEE Transactions on Cloud Computing, vol. 11, no. 1, pp. 897-910, 1 Jan.-March 2023}
\href{https://ieeexplore.ieee.org/document/9573291}{Fixed-point Iterations Approach to Spark Scalable Performance Modeling and Evaluation}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

%\section{Awards} 
%
%\begin{tabular}{rll}
%2014	 & top 52/2500 & KPCB Engineering Fellow\\
%2014	 & 2\textsuperscript{nd} most points & Google Code Jam, Qualification Round\\
%2014	 & 1\textsuperscript{st}/50 & Microsoft Coding Competition, Cornell\\
%2013	 & National & Jump Trading Challenge Finalist\\
%2013 & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament \\
%2012 & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011 & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%2010 & National & Comp. Soc. of India's National Programming Contest\\
%\end{tabular}
%
%\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------

%\section{Societies} 
%
%\begin{tabular}{rll}
%2014 & top 12\%ile & Tau Beta Pi Engineering Honor Society\\
%2014 & National & The Global Leadership and Education Forum (tGELF)\\
%2012 & National & Golden Key International Honor Society\\
%2012 & National & National Society of Collegiate Scholars\\
%\end{tabular}
%
%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}